\bf A Unitary RG-based Auxiliary Model Approach to Strongly-Correlated Electrons

### 2025-02-27 TilingProjectDraft/tilingProject.tex
added entanglement plots

@@

	\pi G_R^\prime(\omega) = P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega}~.

@@

The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function. Exchanging \(G_R^{\prime\prime}\) for \(A\) gives

@@

	G_R^\prime(\omega) = -P\int_{-\infty}^{\infty}d\omega^\prime~\frac{A(\omega^\prime)}{\omega^\prime - \omega}~.

@@

This provides a way of calculating the real part of the Greens function if the spectral function is already known.

>>>>

\subsection{Entanglement entropy and Mutual information}
\begin{figure}[htpb]
	\includegraphics[width=0.24\textwidth]{S_k-1.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-2.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-3.pdf}
	\includegraphics[width=0.24\textwidth]{S_k-4.pdf}
\end{figure}
\begin{figure}[htpb]
	\centering
	\includegraphics[width=0.24\textwidth]{I2_k_N-1.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-2.pdf}
	\includegraphics[width=0.24\textwidth]{I2_k_N-3.pdf}
	% \includegraphics[width=0.24\textwidth]{I2_k_N-4.pdf}
\end{figure}

@@

	G_R^\prime(\omega) = \frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{G_R^{\prime\prime}(\omega^\prime)}{\omega^\prime - \omega} = - \mathcal{H}\left[G_R^{\prime\prime}(\omega)\right] ~,

@@

where \(\mathcal{H}\left[g(\omega)\right]=\frac{1}{\pi}P\int_{-\infty}^{\infty}d\omega^\prime~\frac{g(\omega^\prime)}{\omega - \omega^\prime}\) is the Hilbert transform of the function \(g(\omega)\). The spectral function was defined above as \(-1/\pi\) times the imaginary part of the Greens function. Exchanging \(G_R^{\prime\prime}\) for \(A\) gives

@@

	G_R^\prime(\omega) = \pi \mathcal{H}\left[A(\omega)\right]~.

@@

This provides a method for calculating the real part of a Greens function if the spectral function is already known.
